A Formal Model of Checked C

### 2023-04-06 sandp23/introduction.tex
Intro first draft ready

We propose a type directed partitioning through untrusted types.
Specifically, we introduce~\textbf{tainted} (\taintt) qualifiers that can be used to annotate pointer types or functions. 
The tainted types form the untrusted partition or~\umode~\emph{region} (can only access tainted types), and the non-tainted types will be the trusted partition or~\cmode~\emph{region} (has complete access).
Through static type checking, our type system ensures that tainted types cannot directly affect untainted types.
After successful type checking,~\systemname{} creates two sets of source files~\ucregion{} and~\cregion{} containing tainted and untainted entities, respectively.

These sets of source files will be compiled using~\systemname{} compiler, which enforces the desired isolation through instrumentation.
Developers can choose a specific isolation mechanism.
We explore four different isolation mechanisms with varying guarantees and performance overhead (CITE SECTION).
For instance,~\isoheap{} provides safety against spatial and temporal violations of tainted pointers with almost no performance overhead.
Whereas~\sandbox{} isolation provides complete~\ac{SFI} with~\avgsandboxoverhead{} runtime overhead.

@@

@@

>>>>

We propose a type directed partitioning through untrusted types.
Specifically, we introduce~\textbf{tainted} (\taintt) qualifiers that can be used to annotate pointer types or functions. 
The tainted types form the untrusted partition or~\umode~\emph{region} (can only access tainted types), and the non-tainted types will be the trusted partition or~\cmode~\emph{region} (has complete access).
Through static type checking, our type system ensures that tainted types cannot directly affect untainted types.
After successful type checking,~\systemname{} creates two sets of source files:~\ucregion{} and~\cregion{}, containing tainted and untainted entities, respectively.

These sets of source files will be compiled using~\systemname{} compiler, which enforces the desired isolation through instrumentation.
Developers can choose a specific isolation mechanism.
We explore four different isolation mechanisms with varying guarantees and performance overhead (CITE SECTION).
For instance,~\isoheap{} provides safety against spatial and temporal violations of tainted pointers with almost~\emph{no} performance overhead.
Whereas~\sandbox{} isolation provides complete~\ac{SFI} with~\avgsandboxoverhead{} runtime overhead.

@@

\myparagraph{\systemname Type System and Formalism}
We designed and implemented a flexible program partition technique using tainted types.
Our type system guarantees that the tainted pointers cannot affect untainted pointers and partition the given code into~\ucregion (containing only tainted entities) and~\cregion (CITE SECTION).
We provide formal proof of the~\emph{clean separation theorem} that guarantees that code in ~\cregion will be separated from~\ucregion according to the target isolation mechanism (CITE SECTION).
We also integerated~\systemname{} with~\checkedc that provides additional~\emph{non-crashing} and \emph{non-exposure} guarantees (CITE SECTION).

\myparagraph{Flexible Isolation Mechanisms and Implementation}
We designed four isolation mechanisms with varying guarantees and performance overhead, providing flexibility in choosing a desired isolation mechanism (CITE SECTION).
We implemented our type system (CITE SECTION) and flexible partitioning (CITE SECTION) by modifying~\clang{} compiler.

\myparagraph{Evaluation}
Our evaluation on ...

We made our implementation and datasets open-source to foster future research.

\iffalse

@@

\fi
